### 2020-09-21 paper/appendA.tex
Overweekend fixes

\section{Introduction}
We give a brief overview of the square-free perfect graph coloring algorithm and a pseudocode thereof. The work is not intended to be self-contained and will be impossible to fully understand without \cite{coloringSquareFree} at hand. But when reading \cite{coloringSquareFree}, one may pose a question of what sort of an algorithm emerges from it, and we believe the pseudocode below gives a first overview and is a major step required before an attempt to implement it would be made. For some, looking at the pseudocode could provide a better way to analyze and possibly simplify the algorithm.

@@

Recall, that a prism (\cref{def:prism}) is a graph consisting of two disjoint triangles and two disjoint paths between them.

\begin{defnTwo}[Artemis graph]
  A graph $G$ is an \emph{Artemis graph} if and only if it contains no odd hole, no antihole of length at least five, and no prism.
\end{defnTwo}

@@

\begin{defnTwo}[subdivision]
  In a graph $G$, subdividing an edge $uv \in E(G)$ means removing the edge $uv$ and adding a new vertex $w$ and two new edges $uw, wv$. Starting with a graph $G$, the effect of repeatedly subdividing edges prioduces a graph $H$ called a \emph{subdivision of $G$}. Note that $V(G) \subseteq V(H)$.
\end{defnTwo}

@@

The algorithm we present is derived from contructive proof of the following two theorems.

@@

\begin{defnTwo}[major neighbor of a prism]
  A vertex $v \in V(G) \setminus K$ is a \emph{major neighbor} of pritm $K$ is and only if it has at least two neighbors in $\{a_1, a_2, a_3\}$ and at least two neighbors in $\{b_1, b_2, b_3\}$.
  \label{def:majorNeiOfPrism}
\end{defnTwo}

@@

\Cref{alg:growHyperprism} for growing hyperprism is based upon the following theorem. Recall that by $K_4$ we denote a clique on 4 vertices.
\begin{theorem}[Lemma 3.3 of \cite{coloringSquareFree}]
  Let $G$ be a berge graph, let $H$ be a hyperprism in $G$ and let $M$ be the set of major neighbors of $H$ in $G$. Let $F$ be a component of $V(G) \setminus(V(H) \cup M)$, such that the set of attachments of $F$ in $H$ is not local. Then one can find in polynomial time one of the following
  \begin{itemize}
    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, such that $V(H) \cup V(P)$ induces a hyperprism,
    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, and for each $i \in \{1, 2, 3\}$ an $i$-rung $R_i$ of $H$, such that $V(P) \cup V(R_1) \cup V(R_2) \cup V(R_3)$ induces the line graph of a bipartite subdivision of $K_4$.
  \end{itemize}
  \label{thm:growingHyperprism}
\end{theorem}

@@

\begin{defnTwo}[major vertex w.r.t. a strip system]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if and only if the set of its neighbors saturates the strip system.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t. some choice of rungs]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if and only if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
\end{defnTwo}

\begin{defnTwo}[subset local w.r.t. a strip system]
  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if and only if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
\end{defnTwo}

@@

\begin{itemize}
	\item $a :\in X$, when $X$ is a set -- let $a$ be equal to any element of $X$,
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
	\item $a - b$, when $a$ and $b$ are vertices -- $a$ and $b$ are neighbors,
	\item $a \cdots b$, when $a$ and $b$ are vertices -- $a$ and $b$ are not neighbors,
	\item $a - X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a neighbor in $X$,
	\item $a \cdots X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a nonneighbor in $X$,
	\item $a \blacktriangleleft  X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is complete to $X$,
	\item $a \ntriangleleft X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is anticomplete to $X$,
	\item $X \setComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is complete to $Y$,
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is anticomplete to $Y$,
	\item $[n]$  -- $\{1, \ldots, n\}$,
	\item \LGBSK -- the line-graph of a bipartite subdivision of $K_4$.
\end{itemize}

>>>>

\section{Introduction}
We give a brief overview of the square-free perfect graph coloring algorithm and a pseudocode thereof. The work is not intended to be self-contained and will be impossible to fully understand without \cite{coloringSquareFree} at hand. But when reading \cite{coloringSquareFree}, one may pose a question of what sort of an algorithm emerges from it, and we believe the pseudocode below gives a first overview and is a step required before an attempt to implement it would be made. Looking at the pseudocode could provide a better way to analyze and possibly simplify the algorithm.

@@

\begin{defnTwo}[prism]
  A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
\end{defnTwo}

Notice that for a graph to contain no odd holes, all three paths in a prism must have the same parity. A prism with all three paths odd is called an \emph{odd prism} and a prism with all three paths even is called an \emph{even prism}.

\begin{defnTwo}[Artemis graph]
  A graph $G$ is an \emph{Artemis graph} if and only if it contains no odd holes, no antiholes of length at least five, and no prisms.
\end{defnTwo}

@@

\begin{defnTwo}[subdivision]
  In a graph $G$, subdividing an edge $uv \in E(G)$ means removing the edge $uv$ and adding a new vertex $w$ and two new edges $uw, wv$. Starting with a graph $G$, the effect of repeatedly subdividing edges produces a graph $H$ called a \emph{subdivision of $G$}. Note that $V(G) \subseteq V(H)$.
\end{defnTwo}

@@

The algorithm we present is derived from a constructive proof of the following two theorems.

@@

\begin{defnTwo}[major neighbor of a prism]
  A vertex $v \in V(G) \setminus K$ is a \emph{major neighbor} of prism $K$ is and only if it has at least two neighbors in $\{a_1, a_2, a_3\}$ and at least two neighbors in $\{b_1, b_2, b_3\}$.
  \label{def:majorNeiOfPrism}
\end{defnTwo}

@@

\Cref{alg:growHyperprism} for growing hyperprism is based upon the following theorem. Recall that by $K_4$ we denote a clique on 4 vertices.
\begin{theorem}[Lemma 3.3 of \cite{coloringSquareFree}]
  Let $G$ be a Berge graph, let $H$ be a hyperprism in $G$ and let $M$ be the set of major neighbors of $H$ in $G$. Let $F$ be a component of $V(G) \setminus(V(H) \cup M)$, such that the set of attachments of $F$ in $H$ is not local. Then one can find in polynomial time one of the following
  \begin{itemize}
    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, such that $V(H) \cup V(P)$ induces a hyperprism,
    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, and for each $i \in \{1, 2, 3\}$ an $i$-rung $R_i$ of $H$, such that $V(P) \cup V(R_1) \cup V(R_2) \cup V(R_3)$ induces the line graph of a bipartite subdivision of $K_4$.
  \end{itemize}
  \label{thm:growingHyperprism}
\end{theorem}

@@

\begin{defnTwo}[major vertex w.r.t.~a strip system]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if and only if the set of its neighbors saturates the strip system.
\end{defnTwo}

\begin{defnTwo}[major vertex w.r.t.~some choice of rungs]
  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if and only if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
\end{defnTwo}

\begin{defnTwo}[subset local w.r.t.~a strip system]
  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if and only if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
\end{defnTwo}

@@

\begin{itemize}
	\item $a :\in X$, when $X$ is a set -- let $a$ be equal to any element of $X$,
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
	\item $a - b$, when $a$ and $b$ are vertices -- $a$ and $b$ are neighbors,
	\item $a \cdots b$, when $a$ and $b$ are vertices -- $a$ and $b$ are not neighbors,
	\item $a - X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a neighbor in $X$,
	\item $a \cdots X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a nonneighbor in $X$,
	\item $a \blacktriangleleft  X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is complete to $X$,
	\item $a \ntriangleleft X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is anticomplete to $X$,
	\item $X \setComplete Y$, when $X$ and $Y$ are sets of vertices -- $X$ is complete to $Y$,
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are sets of vertices -- $X$ is anticomplete to $Y$,
	\item $[n]$  -- $\{1, \ldots, n\}$,
	\item \LGBSK -- the line-graph of a bipartite subdivision of $K_4$.
\end{itemize}

### 2020-09-21 paper/coloringAppendix/algI.tex
Style fixes
Overweekend fixes

\begin{mynameforalgorithm}
  % \myalgorithmcommand
  \SetKwFunction{colorGraph}{\textsc{Color-Graph}}
  \Indm\nonl\colorGraph($G$)\\
  \KwData{$G$ -- square-free Berge graph}
  \KwResult{A $\omega(G)$-coloring of $G$}
  \Indp
  \If(\tcp*[f]{\Cref{thm:getPrism}}){$G$ is an Artemis graph}{
    \Return coloring of an Artemis graph $G$ \tcp*{\Cref{thm:colorArtemis}}
  }
  $H \gets$ an induced prism of $G$ \tcp*{\Cref{thm:getPrism}}
  \TODO{do we get $H$ ready from A.1.1?}

@@

      $M \gets \{v: v$ is a major neighbor of H$\}$\;
      \TODO{how do we get M?}

      $H' \gets$ \textsc{Grow-Hyperprism}$(G, H, M, F)$\;
      \If{$H'$ is  a \LGBSK}{
        $J \gets H'$\;
        $(S, N) \gets$ a $J$-strip system\;
        \TODO{how?}
      }\Else{
        $H \gets H'$\;
      }
    }
    \Else(\tcp*[f]{$H$ is a maximal hyperprism}){
      $M \gets \{v: v$ is a major neighbor of H$\}$\;
      \If{$H$ is an even hyperprism}{
        $P \gets$ \textsc{Good-Partition-From-Even-Hyperprism}$(G, H, M)$
        \textbf{break}
      }
      \Else{
        $P \gets$ \textsc{Goog-Partition-From-Odd-Hyperprism}$(G, H, M)$\;
        \textbf{break}
      }
    }
    \If(\tcp*[f]{a $J$-strip system was encountered}){$J \neq$ \textsc{undefined}}{
      $J', (S', N') \gets$ \textsc{Growing-J-Strip}$(G, J, (S, N))$\;
      $M \gets$ a set of major vertives w.r.t. $(S, N)$\;
      \If{$J', (S', N')$ is a special $K_4$ system}{
        $P \gets$ \textsc{Good-Partition-From-Special-Strip-System}$(G, (S, N), M)$
      }\Else{
        $P \gets$ \textsc{Good-Partition-From-J-Strip-System}$(G, J, (S, N), M)$
      }
    }
  }
  \Return \textsc{Color-Good-Partition}$(G, P)$\;
\end{mynameforalgorithm}

>>>>

\begin{mynameforalgorithm}
  % \myalgorithmcommand
  \SetKwFunction{colorGraph}{\textsc{Color-Graph}}
  \Indm\nonl\colorGraph($G$)\\
  \KwData{$G$ -- square-free Berge graph}
  \KwResult{A $\omega(G)$-coloring of $G$}
  \Indp
  \If(\tcp*[f]{\Cref{thm:getPrism}}){$G$ is an Artemis graph}{
    \Return coloring of an Artemis graph $G$ \tcp*{\Cref{thm:colorArtemis}}
  }
  $H \gets$ an induced prism of $G$ \tcp*{\Cref{thm:getPrism}}

@@

      $M \gets \{v: v$ is a major neighbor of H$\}$\;

      $H' \gets$ \textsc{Grow-Hyperprism}$(G, H, M, F)$\;
      \If{$H'$ is  a \LGBSK}{
        $J \gets H'$\;
        $(S, N) \gets$ a $J$-strip system\;
      }\Else{
        $H \gets H'$\;
      }
    }
    \Else(\tcp*[f]{$H$ is a maximal hyperprism}){
      $M \gets \{v: v$ is a major neighbor of H$\}$\;
      \If{$H$ is an even hyperprism}{
        $P \gets$ \textsc{Good-Partition-From-Even-Hyperprism}$(G, H, M)$
        \textbf{break}
      }
      \Else{
        $P \gets$ \textsc{Goog-Partition-From-Odd-Hyperprism}$(G, H, M)$\;
        \textbf{break}
      }
    }
    \If(\tcp*[f]{a $J$-strip system was encountered}){$J \neq$ \textsc{undefined}}{
      $J', (S', N') \gets$ \textsc{Growing-J-Strip}$(G, J, (S, N))$\;
      $M \gets$ a set of major vertices w.r.t. $(S, N)$\;
      \If{$J', (S', N')$ is a special $K_4$ system}{
        $P \gets$ \textsc{Good-Partition-From-Special-Strip-System}$(G, (S, N), M)$
      }\Else{
        $P \gets$ \textsc{Good-Partition-From-J-Strip-System}$(G, J, (S, N), M)$
      }
    }
  }
  \Return \textsc{Color-Good-Partition}$(G, P)$\;
  \vspace{-5cm}
\end{mynameforalgorithm}

### 2020-09-21 paper/coloringAppendix/algVII.tex
Overweekend fixes

\begin{mynameforalgorithm}
  \SetKwFunction{FindSpecialK}{\textsc{Find-Special-K4-Strip-System}}
	\Indm\nonl\FindSpecialK{$G, J, (S, N), m$}\\
  \KwData{$G$ -- square-free, Berge graph \newline
    $J$ -- a $3$-connected graph with appearance in $G$ \newline
    $(S, N)$ -- a $J$-strip system \newline
    $m \in G \setminus (S, N)$ that is major w.r.t. some choice of rungs of $(S, N)$ but not w.r.t. $(S, N)$
  }
  \KwResult{$(S', N')$ -- A special $K_4$-strip system, or \newline
  $(S'', N'')$ -- a bigger $J$-strip system
  }
  \Indp	
  $X \gets N(m)$\;
  $M \gets$ vertices of $G\setminus V(S,N)$ major w.r.t. $(S,N)$\;
  $M^* \gets$ vertices of $G\setminus V(S,N)$ major w.r.t. some choice of rungs\;
  \Assert[SPGT 8.4]{$J = K_4$}
  $V(J) \gets [4]$\;
  $\forall_{i\neq j \in [4]}$: choose rungs $R_{ij}, R_{ij}$, forming line graphs $L(H)$ and $L(H')$ so that $X$ 
  saturates $L(H)$ but does not saturate $L(H')$\;
  \Assert{$R_{ij} \neq R'_{ij}$ if and only if $\{i, j\} = [2]$}
  $r_{ij}, r_{ji} \gets$ ends of each $R_{ij}$\;
  $r'_{ij}, r'_{ji} \gets$ ends of each $R'_{ij}$\;
  $\forall_{i \in [4]} T_i \gets \{r_{ij}, j \in [4] \setminus \{i\} \}$\;
  $\forall_{i \in [4]} T'_i \gets \{r'_{ij}, j \in [4] \setminus \{i\} \}$\;
  \Assert{$X$ has at least two members in each $T_1, \ldots T_4$}
  \Assert{There is $T'_i$ that contains at most one member of $X$}
  \Assert{$T_3 = T'_3, T_4 = T'_4$}
  relabel 1 and 2 in $J$, so that $|X \cap T_1| = 2$ and $|X \cap T'_1| = 1$\;
  \Assert{$r_{12} \in X, r'_{12} \notin X$}
  \Assert{$r_{13} \in X \xor r_{14} \in X$}
  relabel 3 and 4 in $J$, so that $r_{13} \in X, r_{14} \notin X$\;
  \Assert[6.3.(3)]{$R_{34}$ is even and $[X \cap V(L(H'))] \setminus V(R_{34}) = \{r_{31}, r_{32}, r_{41}, r_{42} \}$}
  \Assert[6.3.(4)]{$R_{14}$ has odd length, $r_{21} \in X$}
  \Assert[6.3.(5)]{$R_{12}$ has length $0$, every $12$-rung has even length}
  \Assert[6.3.(6)]{$R_{24}$ has length $0$ and $R_{23}$ has odd length}
  \Assert[6.3.(7)]{Every $34$-rung has non-zero even length}
  $\forall_{i \neq j \in [4]} O_{ij} \gets$ set of vertices that are not major w.r.t $L(H')$ and
  are complete to $(T'_i \cup T'_j) \setminus R'_{ij}$\;
  \Assert{$r_{12} = r_{21} \in O_{12}$, $m \in O_{34}$}
  \Assert{$O_{34} = M^* \setminus M$}
  $(S', N') \gets$ strip system obtained from $(S, N)$ by replacing $S_{12}$ with $S_{12} \setminus O_{12}$\;
  \If{$\exists_{rung R}: $ adding $R$ to $S'_{12}$ produces enlargement of $(S, N)$}{
    \Return $(S'', N'')$ -- an enlargement of $(S, N)$\;
  }
  \Else{
    \Return $(S', N')$ -- a special $K_4$ strip system\;
  }
  \vspace{-10cm}
\end{mynameforalgorithm}

>>>>

\begin{mynameforalgorithm}
  \SetKwFunction{FindSpecialK}{\textsc{Find-Special-K4-Strip-System}}
	\Indm\nonl\FindSpecialK{$G, J, (S, N), m$}\\
  \KwData{$G$ -- square-free, Berge graph \newline
    $J$ -- a $3$-connected graph with appearance in $G$ \newline
    $(S, N)$ -- a $J$-strip system \newline
    $m \in G \setminus (S, N)$ that is major w.r.t.~some choice of rungs of $(S, N)$ but not w.r.t. $(S, N)$
  }
  \KwResult{$(S', N')$ -- A special $K_4$-strip system, or \newline
  $(S'', N'')$ -- a bigger $J$-strip system
  }
  \Indp	
  $X \gets N(m)$\;
  $M \gets$ vertices of $G\setminus V(S,N)$ major w.r.t.~$(S,N)$\;
  $M^* \gets$ vertices of $G\setminus V(S,N)$ major w.r.t.~some choice of rungs\;
  \Assert[\cite{MC06} 8.4]{$J = K_4$}
  $V(J) \gets [4]$\;
  $\forall_{i\neq j \in [4]}$: choose rungs $R_{ij}, R_{ij}$, forming line graphs $L(H)$ and $L(H')$ so that $X$ 
  saturates $L(H)$ but does not saturate $L(H')$\;
  \Assert{$R_{ij} \neq R'_{ij}$ if and only if $\{i, j\} = [2]$}
  $r_{ij}, r_{ji} \gets$ ends of each $R_{ij}$\;
  $r'_{ij}, r'_{ji} \gets$ ends of each $R'_{ij}$\;
  $\forall_{i \in [4]} T_i \gets \{r_{ij}, j \in [4] \setminus \{i\} \}$\;
  $\forall_{i \in [4]} T'_i \gets \{r'_{ij}, j \in [4] \setminus \{i\} \}$\;
  \Assert{$X$ has at least two members in each $T_1, \ldots T_4$}
  \Assert{There is $T'_i$ that contains at most one member of $X$}
  \Assert{$T_3 = T'_3, T_4 = T'_4$}
  relabel 1 and 2 in $J$, so that $|X \cap T_1| = 2$ and $|X \cap T'_1| = 1$\;
  \Assert{$r_{12} \in X, r'_{12} \notin X$}
  \Assert{$r_{13} \in X \xor r_{14} \in X$}
  relabel 3 and 4 in $J$, so that $r_{13} \in X, r_{14} \notin X$\;
  \Assert[6.3.(3)]{$R_{34}$ is even and $[X \cap V(L(H'))] \setminus V(R_{34}) = \{r_{31}, r_{32}, r_{41}, r_{42} \}$}
  \Assert[6.3.(4)]{$R_{14}$ has odd length, $r_{21} \in X$}
  \Assert[6.3.(5)]{$R_{12}$ has length $0$, every $12$-rung has even length}
  \Assert[6.3.(6)]{$R_{24}$ has length $0$ and $R_{23}$ has odd length}
  \Assert[6.3.(7)]{Every $34$-rung has non-zero even length}
  $\forall_{i \neq j \in [4]} O_{ij} \gets$ set of vertices that are not major w.r.t~$L(H')$ and
  are complete to $(T'_i \cup T'_j) \setminus R'_{ij}$\;
  \Assert{$r_{12} = r_{21} \in O_{12}$, $m \in O_{34}$}
  \Assert{$O_{34} = M^* \setminus M$}
  $(S', N') \gets$ strip system obtained from $(S, N)$ by replacing $S_{12}$ with $S_{12} \setminus O_{12}$\;
  \If{$\exists_{rung R}: $ adding $R$ to $S'_{12}$ produces enlargement of $(S, N)$}{
    \Return $(S'', N'')$ -- an enlargement of $(S, N)$\;
  }
  \Else{
    \Return $(S', N')$ -- a special $K_4$ strip system\;
  }
  \vspace{-10cm}
\end{mynameforalgorithm}

### 2020-09-21 paper/coloringAppendix/algVIa.tex
Algos and KT fixes
Style fixes
Overweekend fixes

\subsubsection{Notes}
\begin{itemize}
	\item $T_{uv} := N_u \cap N_v$
	\item Strip $S_{uv}$ is \emph{rich} iff $S_{uv} \setminus T_{uv} \neq \emptyset$
\end{itemize}

\begin{algorithm}
	\SetKwFunction{GoodPartitionJStrip}{\textsc{Good-Partition-From-J-Strip-System}}
	\Indm\nonl\GoodPartitionJStrip{$G, J, (S, N), M$}\\
	\KwData{$G$ -- square-free, Berge graph \newline
		$J$ -- a maximal $3$-connected graph with appearance in $G$ \newline
		$(S, N)$ -- a maximal $J$-strip system \newline
		$M$ -- a set of major vertices w.r.t. $(S, N)$
	}
	\KwResult{A good partition of $G$}
	\Indp	
	$S^*_{uv} \gets S_{uv} \cup$ $($ components of $G\setminus V(S,N)$ that attach in $S_{uv}$ only $)$\;
	$T_{uv} \gets N_u \cap N_v$\;
	\Assert{$T_{uv} \setComplete N_u \setminus N_{uv}$, $T_{uv} \setComplete N_v \setminus N_{vu}$}
	\Assert{$M \cup T_{uv}$ is a clique}
	\If{$\exists S_{uv}$ -- a rich strip in $(S,N)$} {
		\If{$\exists S_{uv}$ -- a rich strip in $(S, N)$, such that
			$M \cup(N_u \setminus N_{uv})$ and $M \cup(N_v \setminus N_{vu})$ are cliques
			}{
			$K_1 \gets N_u \setminus N_{uv}$, $K_2 \gets M \cup T_{uv}$, $K_3 \gets N_v \setminus N_{vu}$\;
			$L \gets (S^*_{uv} \setminus T_{uv}) \cup ($ components of $G\setminus V(S, N)$ that attach only to $N_u$
			and those that attach only to $N_v$ $)$\;
			$R \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup L)$\;
			\Return $(K_1, K_2, K_3, L, R)$\;
		}
		\Else{
			$S_{uv} \gets$ a rich strip in $(S, N)$, such that
			$M \cup(N_u \setminus N_{uv})$ is not a clique and $M \cup(N_v \setminus N_{vu})$ is a clique \;
			$K_1 \gets N_{uv} \setminus T_{uv}$, $K_2 \gets M \cup T_{uv}$, $K_3 \gets N_v \setminus N_{vu}$\;
			$R \gets (S^*_{uv} \setminus N_u) \cup ($ components of $G\setminus V(S,U)$ that attach only to $N_v$ $)$\;
			$L \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup R)$\;
			\Return $(K_1, K_2, K_3, L, R)$\;
		}
	}
	\Else {
		\Assert{$\forall uv \in E(J): S_{uv} = T_{uv}, S_{uv}$ is a clique}
		$S_{uv} \gets $ any strip\;
		$K_1 \gets N_u \setminus S_{uv}$, $K_2 \gets M$, $K_3 \gets N_v \setminus S_{uv}$\;
    $L \gets S^*_{uv} \cup ($ components of $G\setminus V(S,N)$ that attach only to $N_u$ and only to $N_v$ $)$\;
		$R \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup L)$\;
		\Return $(K_1, K_2, K_3, L, R)$\;
	}
\end{algorithm}

>>>>

\begin{mynameforalgorithm}
	\SetKwFunction{GoodPartitionJStrip}{\textsc{Good-Partition-From-J-Strip-System}}
	\Indm\nonl\GoodPartitionJStrip{$G, J, (S, N), M$}\\
	\KwData{$G$ -- square-free, Berge graph \newline
		$J$ -- a maximal $3$-connected graph with appearance in $G$ \newline
		$(S, N)$ -- a maximal $J$-strip system \newline
		$M$ -- a set of major vertices w.r.t.~$(S, N)$
	}
	\KwResult{A good partition of $G$}
	\Indp	
	$S^*_{uv} \gets S_{uv} \cup$ $($ components of $G\setminus V(S,N)$ that attach in $S_{uv}$ only $)$\;
	$T_{uv} \gets N_u \cap N_v$\;
	\Assert{$T_{uv} \setComplete N_u \setminus N_{uv}$, $T_{uv} \setComplete N_v \setminus N_{vu}$}
	\Assert{$M \cup T_{uv}$ is a clique}
	Strip $S_{uv}$ is \emph{rich} if and only if $S_{uv} \setminus T_{uv} \neq \emptyset$\;
	\If{$\exists S_{uv}$ -- a rich strip in $(S,N)$} {
		\If{$\exists S_{uv}$ -- a rich strip in $(S, N)$, such that
			$M \cup(N_u \setminus N_{uv})$ and $M \cup(N_v \setminus N_{vu})$ are cliques
			}{
			$K_1 \gets N_u \setminus N_{uv}$, $K_2 \gets M \cup T_{uv}$, $K_3 \gets N_v \setminus N_{vu}$\;
			$L \gets (S^*_{uv} \setminus T_{uv}) \cup ($ components of $G\setminus V(S, N)$ that attach only to $N_u$
			and those that attach only to $N_v$ $)$\;
			$R \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup L)$\;
			\Return $(K_1, K_2, K_3, L, R)$\;
		}
		\Else{
			$S_{uv} \gets$ a rich strip in $(S, N)$, such that
			$M \cup(N_u \setminus N_{uv})$ is not a clique and $M \cup(N_v \setminus N_{vu})$ is a clique \;
			$K_1 \gets N_{uv} \setminus T_{uv}$, $K_2 \gets M \cup T_{uv}$, $K_3 \gets N_v \setminus N_{vu}$\;
			$R \gets (S^*_{uv} \setminus N_u) \cup ($ components of $G\setminus V(S,U)$ that attach only to $N_v$ $)$\;
			$L \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup R)$\;
			\Return $(K_1, K_2, K_3, L, R)$\;
		}
	}
	\Else {
		\Assert{$\forall uv \in E(J): S_{uv} = T_{uv}, S_{uv}$ is a clique}
		$S_{uv} \gets $ any strip\;
		$K_1 \gets N_u \setminus S_{uv}$, $K_2 \gets M$, $K_3 \gets N_v \setminus S_{uv}$\;
    $L \gets S^*_{uv} \cup ($ components of $G\setminus V(S,N)$ that attach only to $N_u$ and only to $N_v$ $)$\;
		$R \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup L)$\;
		\Return $(K_1, K_2, K_3, L, R)$\;
	}
\vspace{-1cm}
\end{mynameforalgorithm}
